Review of Polymer Solutions for Near-Field Electrospinning with Spatial Control

### 2019-06-20 NFES_Review/article.tex
update

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}
\begin{keyword} 
      polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
\end{keyword}

@@

\section{Introduction}
Diverse polymer patterning techniques have been developed for the fabrication of nano-fibers, such as arc discharge [31], chemical vapor deposition, laser ablation [21], and vapor growth [18]. Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required. The electrospinning method (invented by Formhals Anton in 1934)can produce fibers with a range of diameters between 10 nm and 10 mm [12,2] from a polymer solution under the influence of an electrostatic force. The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry [1, 14, 4, 26].

Even though electrospinning is an old invention [2], it is currently a trending topic among researchers [11, 22, 23]. One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers. The technique allows the production of thin continuous fibers with ease, with diameters down to 3 nm in some cases, which is something difficult to achieve by other techniques. Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials. The produced fibers can be aligned or unaligned. Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques. On the other hand, the understanding of the electrospinning process has improved in the last years [15]. As Reneker and Yarin state: "Electrospinning has rapidly changed fiber making from a capital intensive, large scale process to a low cost, broadly applicable method that manufactures fibers on a laboratory bench, to serve diverse needs ranging from materials science and technology to life sciences and clinical medicine.`` [22]

The main components of the electrospinning technique are the fluid control unit (e.g. syringe pump) and a DC power supply. The process also requires a target electrode or combination of electrodes on which the fibers can be collected. Figure 6.2 describes a typical electrospinning set-up. [15] Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning. [7] Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning. [19] The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher precision when patterning. Figure 6.3 shows a typical near field mechano-electrospinning apparatus.

\section{NFES}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

  \textbf{Solution Concentration:} 7$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 200$\mu m $ and inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:}\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 1.5 $kV $ and dispensed at 600$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 120$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 709$\pm $131$nm $; 49-74$nm $ when applied voltage is 800$V $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{ Not determined} \mbox{}\protect\newline \textbf{Notes:} 108$m $ yield in 15$min $ with a fiber diameter of 709$\pm $131$nm $ &

@@

  \textbf{Solution Concentration:} 6$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:}\textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} 1200$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 7.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 2 $kV $ and dispensed at 0.8-1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} around 400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 200-350$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 5$\mu m $ &

@@

  \textbf{Solution Concentration:} 17$wt\% $ PVDF; 1.7$g $ of PVDF, 5$g $ of acetone, 0.5$g $ of Capstone FS-66, 5$g $ of DMSO \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 14$\;nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 750$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} A4 size commercial printing paper (Double A) \mbox{}\protect\newline \textbf{Applied voltage:} 1.9$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:}\textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

@@

  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:}\textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} Si \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 25$\mu m $ &

@@

  \textbf{Solution Concentration:} 5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} four-nozzle and six-nozzle array with needle spacing changes from 1.5$mm $ to 3.5$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 1-3$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:}\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 1.7-2.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.47$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 3-5 $mm $ &

@@

  \textbf{Solution Concentration:}5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 0.18$mm $ and outer diameter of 0.36$mm $; with needle spacing changes from 2.0$mm $ to 3.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 3.0-4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 2.0-3.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 218-326$\mu m $ &

@@

  \textbf{Solution Concentration:} 2$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} G30 needle with inner diameter of 0.15$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1-3$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1250$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 20$\mu m $ &

@@

  \textbf{Solution Concentration:} 11$wt\% $ gelatin, 30$wt\% $ water, 35.4$wt\% $ acetic acid, 23.6$wt\% $ ethyl acetate \mbox{}\protect\newline \textbf{Nozzle:} 19G needle tip with outer diameter of 1.08$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1.25$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(Dimethylsiloxane) (PDMS) films \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} around 2-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 40$\mu m $ &

@@

  \textbf{Solution Concentration:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle:} nozzle-free \mbox{}\protect\newline \textbf{Solution deposition rate:} The drop reservoir is placed directly on a flat substrate \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} Taylor's cone is focused and put in direct contact with the collector \mbox{}\protect\newline \textbf{Substrate composition:} Poly(tetrafluoroethylene) (PTFE) coated glass slide \mbox{}\protect\newline \textbf{Applied voltage:} pyro-electric field of between 2.7 $x10^{7}\;V/m $ and 5.5$x10^{7}\;V/m $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 304.7$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

@@

  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline $\mu m $$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:}\textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:}\textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

>>>>

\begin{abstract}
Near-field electrospinning (NFES) is identified to be a technique able to fabricate polymer nano and micro fibers with accurate placement. In the past years (2006-2019), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process. Each NFES variant intents to tailor the process parameters in order to improve the fibers' properties. This paper presents a review on the research and related development of electrospun fibers, emphasizing the used polymers, solvents, and fiber characteristics. Relevant summary of polymer solutions and near-field electrospinning processing conditions is provided in this paper.
\end{abstract}
\begin{keyword} 
      polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
\end{keyword}

@@

\section{Introduction}
Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}. One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers. The technique allows the production of thin continuous fibers with ease, with diameters down to 3 nm in some cases, which is something difficult to achieve by other techniques. Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials. The produced fibers can be aligned or unaligned. Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques. On the other hand, the understanding of the electrospinning process has improved in the last years \unskip~\cite{527120:12073538}.

The main components of the electrospinning technique are the fluid control unit (e.g. syringe pump) and a voltage power supply. The process also requires a target electrode or combination of electrodes on which the fibers can be collected. Figure 6.2 describes a typical electrospinning set-up \unskip~\cite{527120:12073538}. Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}. Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}. Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control. NFES has suffered several modifications to improve the precision and accuracy of the fiber deposition.

\section{NFES}
\unskip~\cite{527120:11973130}

\unskip~\cite{527120:11974314}

\unskip~\cite{527120:11974329}

\unskip~\cite{527120:11974305}

\unskip~\cite{527120:11974306}

\unskip~\cite{527120:11974308}

\unskip~\cite{527120:11974310}

\unskip~\cite{527120:11974311}

\unskip~\cite{527120:11974312}

\unskip~\cite{527120:11974313}

\unskip~\cite{527120:11974316}

\unskip~\cite{527120:11974320}

\unskip~\cite{527120:11974321}

\unskip~\cite{527120:11974322}

\unskip~\cite{527120:11974323}

\unskip~\cite{527120:11974324}

\unskip~\cite{527120:11974325}

\unskip~\cite{527120:11974326}

\unskip~\cite{527120:11974327}

\unskip~\cite{527120:11974328}

\unskip~\cite{527120:11974304}

\unskip~\cite{527120:11974307}

\unskip~\cite{527120:12033655}

\unskip~\cite{527120:12033656}

\unskip~\cite{527120:12033657}

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

@@

  \textbf{Solution Concentration:} 7$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 200$\mu m $ and inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.1$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 1.5 $kV $ and dispensed at 600$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 120$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 709$\pm $131$nm $; 49-74$nm $ when applied voltage is 800$V $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{ Not determined} \mbox{}\protect\newline \textbf{Notes:} 108$m $ yield in 15$min $ with a fiber diameter of 709$\pm $131$nm $ &

@@

  \textbf{Solution Concentration:} 6$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} \textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} 1200$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 7.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} polymer jet initiated at 2 $kV $ and dispensed at 0.8-1$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} around 400$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 200-350$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 5$\mu m $ &

@@

  \textbf{Solution Concentration:} 17$wt\% $ PVDF; 1.7$g $ of PVDF, 5$g $ of acetone, 0.5$g $ of Capstone FS-66, 5$g $ of DMSO \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 14$\;nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 750$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} A4 size commercial printing paper (Double A) \mbox{}\protect\newline \textbf{Applied voltage:} 1.9$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

@@

  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} \textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} Si \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 25$\mu m $ &

@@

  \textbf{Solution Concentration:} 5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} four-nozzle and six-nozzle array with needle spacing changes from 1.5$mm $ to 3.5$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 1-3$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 1.7-2.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.47$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 3-5 $mm $ &

@@

  \textbf{Solution Concentration:}5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 0.18$mm $ and outer diameter of 0.36$mm $; with needle spacing changes from 2.0$mm $ to 3.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 3.0-4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition: } \textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 2.0-3.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 218-326$\mu m $ &

@@

  \textbf{Solution Concentration:} 2$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} G30 needle with inner diameter of 0.15$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1-3$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1250$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 20$\mu m $ &

@@

  \textbf{Solution Concentration:} 11$wt\% $ gelatin, 30$wt\% $ water, 35.4$wt\% $ acetic acid, 23.6$wt\% $ ethyl acetate \mbox{}\protect\newline \textbf{Nozzle:} 19G needle tip with outer diameter of 1.08$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1.25$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(Dimethylsiloxane) (PDMS) films \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} around 2-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 40$\mu m $ &

@@

  \textbf{Solution Concentration:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle:} nozzle-free \mbox{}\protect\newline \textbf{Solution deposition rate:} The drop reservoir is placed directly on a flat substrate \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} Taylor's cone is focused and put in direct contact with the collector \mbox{}\protect\newline \textbf{Substrate composition:} Poly(tetrafluoroethylene) (PTFE) coated glass slide \mbox{}\protect\newline \textbf{Applied voltage:} pyro-electric field of between 2.7 $x10^{7}\;V/m $ and 5.5$x10^{7}\;V/m $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 304.7$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

@@

  \textbf{Solution Concentration:} SU-8/PEO/TBF blend with 0.75$wt\% $ PEO, 1$wt\% $ TBF; the blend is diluted with 30$vol\% $ DMF \mbox{}\protect\newline $\mu m $$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} \textit{Not determined} \mbox{}\protect\newline \textbf{Substrate composition:} Brass disk with a diameter of 38$mm $ \mbox{}\protect\newline \textbf{Applied voltage:} 980$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
